Hydras \& Co.

### 2022-09-30 doc/hydras.tex
minor changes
sart a new chapter on Goedel encoding (after Russel)
update acknowledgments

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800\\ \textbf{email:} pierre dot casteran arobas gmail dot com. \\ With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions was originally authored by Russel O'Connor.}%\cite{OConnor05}.}

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean, Jéremy Damour,   Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Cl\'ement Pit-Claudel, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this library and  document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

@@

\emph{\color{red!80}This maintenance job has just started, ant will probably be long to complete. Help will be welcome!}

\include{chapter-primrec}

>>>>

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800\\ \textbf{email:} pierre dot casteran arobas gmail dot com. \\ With contributions by Yves Bertot, Ilm\={a}rs C\={i}rulis, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions was originally authored by Russel O'Connor.}%\cite{OConnor05}.}

@@

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, Ilm\={a}rs C\={i}rulis, \'Evelyne Contejean, Jéremy Damour,   Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Cl\'ement Pit-Claudel, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this library and  document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

@@

\emph{\color{red!80}This maintenance job has just started, and will probably be long to complete. Help is welcome!}

\include{chapter-primrec}
\include{chapter-encoding}
